Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-18 paper/main.tex
Small fix

% Bland-Altman-Plots
To illustrate the similarity of correlates of spatial processing in
naturalistic (audio-description) and conventional stimulation, independent of a
particular cluster-forming threshold, Bland-Altman plots for all participants
are shown in Figure.~\ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of all voxels in temporal and occipital cortices. The marginal distributions
of the mean scores indicate a general agreement of both contrast scores across
voxels in the PPA localization overlap as a probabilistic indicator (blue), and the
individual block-design localizer results (red). Notably, 11 participants exhibit
a pattern of increased $Z$-scores for the naturalistic stimulus (lower right
quadrant) that includes voxels labeled by the block-design localizer, but
also additional voxels.

>>>>

% Bland-Altman-Plots
To illustrate the similarity of correlates of spatial processing in
naturalistic (audio-description) and conventional stimulation, independent of a
particular cluster-forming threshold, Bland-Altman plots for all participants
are shown in Figure~\ref{fig:bland-altman}.
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus audio-description) of all voxels in temporal and occipital cortices. The marginal distributions
of the mean scores indicate a general agreement of both contrast scores across
voxels in the PPA localization overlap as a probabilistic indicator (blue), and the
individual block-design localizer results (red). Notably, 11 participants exhibit
a pattern of increased $Z$-scores for the naturalistic stimulus (lower right
quadrant) that includes voxels labeled by the block-design localizer, but
also additional voxels.
